|

### 2023-12-11 paper/paper.qmd
Change editor to 'source'

format: 
   html:
      df-print: kable
   docx:
      df-print: kable
      toc: false
include-in-header:
  - text: |
      <style>
      h1 {
        text-align: center;
      }
      </style>
crossref:
  sec-prefix: "Sectie"
editor: visual
css: paper.css
title-block-banner: true
bibliography: references.bib
toc: true
toc-depth: 4
toc-location: left
tbl-cap-location: bottom
fig-cap-location: bottom
number-sections: true
reference-location: margin
csl: chicago-author-date.csl
execute:
  echo: false
lang: nl
manuscript: false
---

>>>>

format: 
   html:
      df-print: kable
   docx:
      df-print: kable
      toc: false
include-in-header:
  - text: |
      <style>
      h1 {
        text-align: center;
      }
      </style>
crossref:
  sec-prefix: "Sectie"
editor: source
css: paper.css
title-block-banner: true
bibliography: references.bib
toc: true
toc-depth: 4
toc-location: left
tbl-cap-location: bottom
fig-cap-location: bottom
number-sections: true
reference-location: margin
csl: chicago-author-date.csl
execute:
  echo: false
lang: nl
manuscript: false
---
